---
title: "Winter Olympics 2022 Project proposal"
author: "Sam, Amy, Dylan"
output: github_document
---

```{r load-packages, message = FALSE}
library(tidyverse)
library(broom)
```

## 1. Introduction
For our final project, we have decided to investigate medal counts, specifically comparing First World vs Third World countries. This question will allow us to investigate how funding affects performance at the Olympics. For First World countries such as the US and Australia, there is more disposable income that can be attributed to athletics. This funding can help hire better coaches, build better facilities and equipment. Our data set is from Kaggle which is a website where data scientists upload data sets for public use. Our data set includes 2800 athletes with 15 disciplines, and 91 nations participating in the Winter Olympics 2022. The dataset was updated every 2-3 days with the new medals awarded and was finally updated when the Olympics ended on February 20th.  

General research Question: How does funding affect Olympic medals gained by countries, specifically first world vs third world?

Sub Questions:
How many medals are gained by each country, bronze, silver, and gold?
Country income contributed to athletes?
Which countries are considered third world?
How many athletes by country?
Correlation between medals and income?



## 2. Data

```{r load-data}
View(Athletes)
View(CountryTemp)
View(Entries_By_Discipline)
View(Medals12)
View(Teams)
View(gapminder)

```


## 3. Data analysis plan
X = income, y = medal (gold, silver, bronze), dots = country by color
Other explanatory values may include average income, average athletes by discipline



